Generating Images From Captions\\ With Attention

### 2015-10-08 ram_workshop/ram-paper.tex
small errors

\section{Introduction}
Statistical natural image modelling remains a fundamental problem in computer vision and image understanding. Despite the advances in the variational generative models \cite{kingma_vae}\cite{gregor_draw} and the Generative Adversarial Networks (GANs) \citep{goodfellow_gan}\cite{denton_lapgan}, image generative models studied previously, are often restricted to learning unconditional models of images distribution or conditioned on simple structured annotations, for example classification labels. In real world, however, images rarely appear in isolation. They often accompanied by their unstructured textual descriptions on web pages and in books. The additional information from image and unstructured text description could be used to simplify the image modelling task. Moreover, learning generative models conditioned on text also allows better understand of the generalization performance of the model as we can create textual descriptions of completely new scenes not seen at training time.

@@

In this paper, we address the problem of image generation from unstructured natural language captions. By extending the Deep Recurrent Attention Writer (DRAW)\cite{gregor_draw}, our model iteratively draws patches on canvas, while attending to the relevant words in the description. Overall, the main contributions of this work are the following: we introduce a conditional alignDRAW model, a generative model of images from captions using a soft attention mechanism. The images generated by our alignDRAW model are refined in a post-processing step by a deterministic Laplacian pyramid adversarial network \cite{denton_lapgan}. We then illustrate how our method, learnt on Microsoft COCO, generalizes to the captions describing novel scenarios that is previously unseen from the dataset.

>>>>

\section{Introduction}
Statistical natural image modelling remains a fundamental problem in computer vision and image understanding.
Despite advances in variational generative models \cite{kingma_vae}\cite{gregor_draw} and Generative Adversarial Networks (GANs) \citep{goodfellow_gan}\cite{denton_lapgan}, 
generative models of images studied previously often defined distributions that were restricted to being either unconditioned or conditioned on simple structured annotations, for example classification labels.
In real world applications, however, images rarely appear in isolation as they are often accompanied by unstructured textual descriptions, such as on web pages and in books. 
The additional information from these descriptions could be used to simplify the image modelling task. Moreover, learning generative models conditioned on text also allows a better understanding of the generalization performance of the model, as we can create textual descriptions of completely new scenes not seen at training time.

@@

In this paper, we address the problem of image generation from unstructured natural language captions. By extending the Deep Recurrent Attention Writer (DRAW)\cite{gregor_draw}, our model iteratively draws patches on a canvas, while attending to the relevant words in the description. Overall, the main contributions of this work are the following: we introduce a conditional alignDRAW model, a generative model of images from captions using a soft attention mechanism. The images generated by our alignDRAW model are refined in a post-processing step by a deterministic Laplacian pyramid adversarial network \cite{denton_lapgan}. We then illustrate how our method, learnt on Microsoft COCO, generalizes to captions describing novel scenarios that are not seen in the dataset.
